Databases are an effective and efficient method for storage and access of mass-spectrometry data

### 2025-06-20 manuscript/manuscript.Rmd
Fixing author list

---
title: "Databases are an effective and efficient method for storage and access of mass-spectrometry data"
author:
  - William Kumler
  - Sam LaRue
  - Anitra E. Ingalls
output: 
  word_document:
    reference_docx: template.docx
bibliography:
- Exported Items.bib
csl: journal-of-proteome-research.csl
---

>>>>

---
title: "Databases are an effective and efficient method for storage and access of mass-spectrometry data"
author:
  William Kumler, Sam LaRue, Anitra E. Ingalls
output: 
  word_document:
    reference_docx: template.docx
bibliography:
- Exported Items.bib
csl: journal-of-proteome-research.csl
---
